The Ising model and the Metropolis Algorithm \\ \hrulefill\small{ FYS3150: Computational Physics }\hrulefill

### 2016-11-22 Project4/article/article.tex
P5: Added file write function. P4: minor changes to article

\section{Algorithm}
An initial spin configuration will be

@@

In order to simulate how the system in this study evolves towards a steady state, Markov chains are used repeatedly in Monte Carlo simulations. From Markov chains one gets tow conditions needed for reaching a steady state, detailed balance and ergodicity. These properties governs our choice of algorithm, the Metropolis-Hastings algorithm.

>>>>

\section{Algorithm}
The algorithm for solving the Ising model consists of several parts and interesting aspects. The path to a steady state for the Ising mode can be seen as a Markov chain, which justifies the use of the Metropolis-Hastings algorithm, which again can be seen as one cycle in a Monte Carlo solver.

@@

In order to simulate how the system in this study evolves towards a steady state, Markov chains are used repeatedly in Monte Carlo simulations. From Markov chains one gets two conditions needed for reaching a steady state, detailed balance and ergodicity. These properties governs our choice of algorithm, the Metropolis-Hastings algorithm.
